---
title: "Test 2"
output: html_notebook
---

| Test 2                         |                Data Analysis with R |
| :---                           |                                ---: |
| Due by 8:00 PM on Thu Nov 2    | Business Analytics Graduate Program |
| Submit via codePost            |                 BAIS:6060 Fall 2023 |

# Instructions

**Submit your completed notebook back to codePost by 8:00 PM.**

*Late policy:* For every 10-minute period your notebook is turned in
past 8:00 PM (including the first 10-minute period), you will lose 25%
of the test points. For example, if `test.Rmd` is turned in at 8:01 PM,
you will lose 25%.

This is an individual exam. No communication with anyone else is
allowed. However, the exam is open-notes and open-Internet. Observe all
rules as specified on the homeworks as usual. As a reminder, please do
not use Excel to save your CSV file.

You should have received the exam materials (including this file,
`test.Rmd`) from GitHub. Complete the exercises below in order. Before
the time limit has expired, upload only your modified `test.Rmd` to codePost.

# Exercises

```{r}

```

## 1 (4 points)

R includes two built-in data frames, `cars` and `iris`. You can see them
by typing "cars" and "iris" in the console. Combine `cars` and `iris`
into a single list called `mylist`. Make sure `cars` comes first in
`mylist`.

```{r}

```

## 2 (4 points)

Scrape the table with column headings "Liquid", "Dry", and "Capacity" at
the webpage

    https://en.wikipedia.org/wiki/Imperial_units

into a data frame called `volume_table`. Just scrape the table; don't do
any post-processing of the data frame.

```{r}

```

## 3 (8 points)

The included file `county_data.csv` contains some data for the 99
counties in Iowa. The `region` column specifies the county code, and
the `v` column specifies the data value of interest. Plot and export a
choropleth map for this data; use `graphic.png` for the filename. Make
sure the plot is zoomed into Iowa.

```{r}

```

## 4 (8 points)

Use a for loop to calculate

    (1/2) + (1/3) + (1/4) + (1/5) + ... + (1/313) + (1/314)

Save the result in an object called `myval`.

```{r}

```

## 5 (8 points)

Create a matrix, called `mat`, with 8 rows and 5 columns, such that
`mat[i, j]` contains the value 0.5*(i + j).

```{r}

```

## 6 (8 points)

If you do `sqrt(-1)` in the console, R gives a warning and returns
`NaN`, which stands for "Not a Number". Write a function called
`mysqrt`, which takes one input and: (a) returns the square root of
that input if the input is nonnegative; (b) returns 0 if the input is
non-numeric or negative.

```{r}

```

## 7 (10 points)

Write a function called `mycap`, which has one formal argument, `mystr`,
and which converts `mystr` to lower case, except that the last character
is capitalized, e.g.,

    mycap(mystr = "Today")           returns    "todaY"
    mycap(mystr = "pRoGrAm")         returns    "prograM"
    mycap(mystr = "ENCYCLOPEDIa")    returns    "encyclopediA"

```{r}

```

## 8 (10 points)

The included data set `bc.csv` contains data on 683 breast-cancer
patients. In particular, the column `Class` contains a "benign" or
"malignant" diagnosis for each patient.

Train and test a `decision_tree` classification model to predict `Class`
from the other columns using a 90%/10% split between the training and
testing data. In `my_metrics_dt`, save the output of `metrics(...)` for
this model.

[Note: The chunk of code below begins with a line `set.seed(1)`. Please
leave this line in place, and put your code below this line.]

```{r}
set.seed(1) # Do not move or remove this line

```
