---
title: "Test 2"
output: html_notebook
---

| Test 2                         |                Data Analysis with R |
| :---                           |                                ---: |
| Due by 8:30 PM on Thu Nov 2    | Business Analytics Graduate Program |
| Submit via codePost            |                 BAIS:6060 Fall 2023 |

# Instructions

**Submit your work to codePost by 8:30 PM. You can only submit it once.**

This is an individual exam. No communication with anyone else is
allowed. However, the exam is open-notes and open-Internet. Observe all
rules as specified on the homeworks as usual. As a reminder, please do
not use Excel to save your CSV files.

You should have received the exam materials (including this file,
`test.Rmd`) from GitHub. Complete the exercises below. Before the time
limit has expired, upload the requested files to codePost.

When done with the six exercises below, create a `solution.R` script file 
and place all R code in it with comments and whitespace. Be sure that it 
is well-formed and runs stand alone, as this is what I will grade.

# Exercises (add all library commands here)

```{r}



```

## 1 (8 points)

Use a for loop to calculate

    (1/2) + (1/3) + (1/4) + (1/5) + ... + (1/313) + (1/314)

Save the result in an object called `myval`. Similar to Homework 1, use `writeLines( )`
to create a text file called `responses.txt` with the first line as "Responses:". 
Add `myval` to `responses.txt` on a new line. Do not close connection yet.

```{r}




```

## 2 (10 points)

R includes two built-in data frames, `cars` and `iris`. You can see them
by typing "cars" and "iris" in the console. Combine `cars` and `iris`
into a single list called `myList`. Make sure `cars` comes first in
`myList`. Add any cars entries to `responses.txt`, where `speed` is greater 
than 20 and `dist` is greater than 100. Each item found should be on its own 
line in `responses.txt` with `speed` value first then `dist` value with a space 
in between the two values. You must use list notation to get credit for this, 
meaning use square bracket notation.

```{r}




```

## 3 (14 points)

Write a function called `mycap`, which has one formal argument, `mystr`,
and which converts `mystr` to lower case, except that the last character
is capitalized, e.g.,

    mycap(mystr = "Today")           returns    "todaY"
    mycap(mystr = "pRoGrAm")         returns    "prograM"
    mycap(mystr = "ENCYCLOPEDIa")    returns    "encyclopediA"
    obj = "First time I've seen a foot-rest in first class"
    mycap(mystr = obj)               returns    <<error>>

Call `mycap` with the above inputs, writing the result to `responses.txt`
with each result on its own line.

Also, add an error handler function called `my.err.handler` that writes
the message, “Function input error due to: <<error>>" to `responses.txt`. 
Execution should not halt if `my.err.handler` is invoked. At the end of 
this code block, close the file connection to `responses.txt`.

```{r}




```

## 4 (8 points)

Create data table, called `dt`, with 8 rows and 5 columns with the names a, b, c, d, e.
Initialize all values to zero at creation. Next, using this notation `dt[i, j]` to 
traverse the table, starting at row 1 column a, change the table values to 0.5*(i + j).
Use write_csv function to write `dt` to file called `dt.csv`.

```{r}




```

## 5 (8 points)

If you do `sqrt(-1)` in the console, R gives a warning and returns
`NaN`, which stands for "Not a Number". Write a function called
`mysqrt`, which takes one input and: (a) returns the square root of
that input if the input is nonnegative; (b) returns 0 if the input is
non-numeric or negative. Call `mysqrt` with input -1, 'a', 25, and 100. 
Put results in data table called `sq`, with one column called `result`. 
Write `sq` to `sq.csv` using write_csv.

```{r}




```

## 6 (12 points)

The included data set `bc.csv` contains data on 683 breast-cancer
patients. In particular, the column `Class` contains a "benign" or
"malignant" diagnosis for each patient.

Train and test a `decision_tree` classification model to predict `Class`
from the other columns using a 90%/10% split between the training and
testing data. In `my_metrics_dt`, save the output of `metrics(...)` for
this model. Use `write_csv` to create text file called `metrics.csv` from
`my_metrics_dt`.

[Note: The chunk of code below begins with a line `set.seed(1)`. Please
leave this line in place, and put your code below this line.]

```{r}

set.seed(1) # Do not move or remove this line




```
